Real-time epidemiological estimates from ONS Community Infection Survey data

### 2022-03-01 docs/report.Rmd
load magick library
use png in report

```{r setup, echo = FALSE, include = FALSE}
library(cowplot)
library(here)

@@

```{r, results = 'asis', echo = FALSE}
for (level in names(estimates)) {
  cat("\n\n#", estimates[[level]], "estimates", "{.tabset}", "\n")
  for (quantity in names(quantities)) {
    cat("\n\n##", quantities[[quantity]], "\n")
    file_name <-
      paste0(level, "_", quantity, "_", time_horizon[[quantity]], ".svg")
    p <- ggdraw() + draw_image(here::here("figures", "additional", file_name))
    print(p)
  }
}
```

>>>>

```{r setup, echo = FALSE, include = FALSE}
library(cowplot)
library(here)
library(magick)

@@

```{r, results = 'asis', echo = FALSE}
for (level in names(estimates)) {
  cat("\n\n#", estimates[[level]], "estimates", "{.tabset}", "\n")
  for (quantity in names(quantities)) {
    cat("\n\n##", quantities[[quantity]], "\n")
    file_name <-
      paste0(level, "_", quantity, "_", time_horizon[[quantity]], ".png")
    p <- ggdraw() + draw_image(here::here("figures", "additional", file_name))
    print(p)
  }
}
```
